### 2021-11-15 NSF2021/Description/specificaim1.tex

Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}

Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

\begin{wrapfigure}[16]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
  }
\end{wrapfigure}
Finally, boundary condition \eqref{eq:bcs}(c) models 
a particle whose head surface repels the tail surface as proposed in
\cite{MaRa76, Ma77}.
The particles initially form chains with their directors perpendicular to the
length of the chain. The equilibrium structure
resembles a checkerboard pattern
where each particle coordinates
its head with the head of three other particles and its tail with the
tail of three other particles Figure~\ref{fig:self-assembly}(c).

>>>>

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}
Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[14]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
  }
\end{wrapfigure}
Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

Finally, boundary condition \eqref{eq:bcs}(c) models 
a particle whose head surface repels the tail surface as proposed in
\cite{MaRa76, Ma77}.
The particles initially form chains with their directors perpendicular to the
length of the chain. The equilibrium structure
resembles a checkerboard pattern
where each particle coordinates
its head with the head of three other particles and its tail with the
tail of three other particles Figure~\ref{fig:self-assembly}(c).
